### 2021-09-08 input/experiments.tex
integrate CDN but not satisfying

@@

This section describes the results of our experimentation evaluating
the properties of \NAME that enables adaptive scoped broadcast in
dynamic networks. It answers the following questions: What is the
overhead of reaching consistent partitioning using \NAME in large
scale networks?  Is \NAME relevant in Edge infrastructures where
\processes are geo-distributed into clusters? We performed the
experimentation using PeerSim, a simulator written in Java that allows
researchers to evaluate and assess distributed algorithms in large
scale networks~\cite{montresor2009peersim}. The code is available on
the Github platform at
\url{https://anonymous.4open.science/r/peersim-partition-5592}.

@@

\begin{figure}
  \centering\includegraphics[width=0.61\columnwidth]{img/as_cast_complexity.eps}
  \caption{\label{fig:complexity}Overhead of dynamic consistent partitioning
    using \NAME.}

@@

\begin{figure}
  \centering\includegraphics[width=0.61\columnwidth]{img/as_cast_geant.eps}
  \caption{\label{fig:geant}Overhead of \NAME in the partitioning of 2 clusters connected by a long distance link.}
\end{figure}

>>>>

\newcommand{\FIGSCALE}{0.59}

@@

%% This section describes the results of our experimentation evaluating
%% the properties of \NAME that enables adaptive scoped broadcast in
%% dynamic networks.

This section aims to answer the following questions about \NAME: What
is the overhead of reaching consistent partitioning using \NAME in
large scale networks?  Is \NAME relevant in Edge infrastructures where
\processes are geo-distributed into clusters? We performed the
experimentation using PeerSim, a simulator written in Java that allows
researchers to evaluate and assess distributed algorithms in large
scale networks~\cite{montresor2009peersim}. The code is available on
the Github platform at
\url{https://anonymous.4open.science/r/peersim-partition-5592}.

@@

\begin{figure}
  \centering\includegraphics[width=\FIGSCALE\columnwidth]{img/as_cast_complexity.eps}
  \caption{\label{fig:complexity}Overhead of dynamic consistent partitioning
    using \NAME.}

@@

\begin{figure}
  \centering\includegraphics[width=\FIGSCALE\columnwidth]{img/as_cast_geant.eps}
  \caption{\label{fig:geant}Overhead of \NAME in the partitioning of 2 clusters connected by a long distance link.}
\end{figure}

### 2021-09-08 input/proposal.tex
integrate CDN but not satisfying

\begin{theorem}[\label{theo:bef}\underline{B}est \underline{e}ventual
    \underline{f}orwarding $(BEF) \implies CP$]
%
Assuming reliable communication links where a correct \process $q$
eventually receives the message $m$ \underline{s}ent to it by a
\process $p$ ($s_{pq}(m) \implies r_{q}(m)$), \processes eventually
reach consistent partitioning if each \process eventually
\underline{f}orwards ($f_p(m) \implies \forall \langle p, q\rangle \in
E: s_{pq}(m)$) its best known partition.
\end{theorem}

@@

\begin{proof}
  % \begin{asparadesc}
  % \item [$BEF \implies CP$:]
  When a \process $s_1$ becomes a source, it belongs to its own
  partition, for there exists no better partition than its own:
  $\forall p \in V: |\Pi_{s_1 s_1}| < |\Pi_{s_1 p}|$. It delivers,
  hence forwards such an $\alpha$ message to its neighbors. Since
  communication links are reliable, neighboring \processes eventually
  receive such a notification $\forall \langle s_1, q \rangle \in E,
  s_1 \in S \iff \eventually r_q(\alpha_{s_1}^{w_{s_1 q}})$. Most
  importantly, whatever the order of received messages, every \process
  $q'$ in this neighborhood -- such that there exists no better
  partition $s_2$ than the received one -- delivers and forwards it:
  $\forall s_2 \in S: |\Pi_{q' s_1}| < |\Pi_{q' s_2}| \implies
  \eventually d_{q'}(\alpha_{s_1}^{w_{s_1 q'}})$. By transitivity, the
  message originating from $s_1$ reaches all such \processes through
  their shortest paths: $\forall q'' \in V, s_1, s_2 \in S: |\Pi_{q''
    s_1}| < |\Pi_{q'' s_2}| \implies \eventually
  d_{q''}(\alpha_{s_1}^{|\Pi_{s_1 q''}|})$.  Since there exists only
  one best sum of weights per \process that can never be retracted,
  \processes eventually reach consistent partitioning.
  %% /!\ not equivalence for there exists other implementations.
  %% \item [$CP \implies BEF$:] By contradiction, if a \process $q \in
  %%   \Pi_{sp} = [s, \ldots, q, q', \ldots, p]$ with $s, q, p \in P_s$
  %%   does not forward its received $\alpha_s^{|\Pi_{sq}|}$, then
  %%   following \processes from $q'$ to $p$ may mistake another
  %%   partition for their  because it needs the weight $W_{pq}$.
  %% \end{asparadesc}
\end{proof}

@@

\begin{theorem}[\label{theo:dcp}BEF$^+$: BEF $\wedge$ (Purge $\rightarrow$ BEF) $\implies$
    \underline{D}ynamic \underline{c}onsistent
    \underline{p}artitioning (DCP)]
%
When a \process can \texttt{Add} and \texttt{Del}ete its partition, to
ensure consistent partitioning, best eventual forwarding (see
Theorem~\ref{theo:bef}) additionally requires
\begin{inparaenum}[(i)]
\item eventual purging of stale messages ($S(m)
  \implies (d_q(m) \implies \eventually d_q(m) \rightarrow
  d_q(m'))$);
\item then best eventual forwarding so such an $m'$ ends up
  originating from the best up-to-date source for $q$.
\end{inparaenum}
\end{theorem}

\begin{proof}
  %% To reach consistent partitioning, the last message delivered by
  %% every process is not stale and comes from its respective best
  %% source: $d(m)$
  Assuming BEF as default propagation behavior where \processes
  deliver and forward the best sum of weights they received. We must
  prove that despite stale messages, the last delivery of every
  \process is the message that followed the shortest path to its
  closest source.
  \begin{asparadesc}
  \item [BEF without Purge:] From Figure~\ref{fig:problemD}, a
    \process may receive messages in such an order ($d_b(\alpha_d^1)
    \rightarrow r_b(\delta_a) \rightarrow d_b(\delta_d)$) that it does
    not forward messages required by other \processes
    ($\delta_a$). The last delivery of some nodes ($c$ and $d$) is
    wrong ($\alpha_a^3$ instead of $\delta_a$). \Processes never reach
    consistent partitioning.
    %% Figure~\ref{fig:proofA} depicts the generic case where a \process
    %% $b$ precludes itself and subsequent \processes such as $c$ of
    %% delivering the message from their respective best source
    %% $a$. \Process $b$ received and delivered a message from a
    %% partition that has since then been deleted but with a better sum
    %% of weights than newly received ones ($\alpha_d^y <
    %% \alpha_a^{x'}$). It forever discards such a message
    %% $\alpha_a^{x'}$.
  \item [Purge not followed by BEF:]
    %% also transiting messages
    Assuming that every \process removes control information as soon
    as it becomes stale ($S(\alpha_a) \implies d_b(\alpha_a^x)
    \rightarrow d_b(\delta_a)$) and cannot deliver stale messages
    anymore ($S(\alpha_a^x) \implies d_c(m_1) \rightarrow \ldots
    \rightarrow d_c(m_k \not\in \alpha_a)$), staleness does not impair
    up-to-date messages propagation. However, even in such settings,
    depending on receipt order ($d_b(\alpha_a^{x}) \rightarrow
    r_b(\alpha_c^{y : y > x}) \rightarrow d_b(\delta_b)$), a \process
    may never receive again, hence deliver and forward a message that
    was received and discarded before ($\alpha_c^{y}$). When such a
    message contains its best up-to-date partition, the \process never
    ends up in its best partition. Therefore, \processes do not reach
    consistent partitioning.
  \item [Purge then BEF:] Assuming the eventual and definitive removal
    of stale messages at each \process, eventually every \process only
    delivers and forwards up-to-date messages, or no message at
    all. Assuming that eventually, each removal triggers the
    forwarding of best delivered messages, every \process eventually
    delivers and forwards the best up-to-date delivered messages.
    %% Removing \emph{forever} all such stale messages about
    %% deleted partitions would allow \processes to propagate their best
    %% up-to-date partition again, eventually reaching consistent
    %% partitioning together, as stated by Theorem~\ref{theo:bef}.
  \end{asparadesc}
  Using BEF$^+$, \processes reach consistent partitioning together as
  in Theorem~\ref{theo:bef}.
\end{proof}

@@

\begin{theorem}[\label{theo:threephase}Three-phase purge]
  The following three phases are sufficient to eventually purge the
  system from stale control information:
  \begin{inparaenum}[(i)]
  \item propagation of delete notifications,
  \item detection of possibly blocking conditions, and
  \item propagation of possibly deleted but blocked notifications.
  \end{inparaenum}
\end{theorem}

@@

  A \process (such as $d$) whose last delivery is $\alpha_X$, but
  whose parent is neither inconsistent (like $b$) nor receiving
  $\delta_X$ (like $a$), eventually receives $\Delta$ from a detecting
  \process, either directly or transitively, for such a child \process
  ($d$) trusts the possible removal of $P_X$ by delivering and
  forwarding such $\Delta$. $\Delta$ suffers from identical blocking
  conditions (between $b$ and $c$) than $\delta$, leading to the same
  solutions of detection and propagation of $\Delta$. Eventually,
  every \process whose last delivery is $\alpha_X$ receives and
  delivers either a better $\alpha_Z$, or $\delta_X$, or $\Delta_X$.

  %% Some \processes may have delivered messages about other partitions
  %% before or after $\alpha_X$. \Processes such as $b$ and $c$ delivered
  %% messages about $P_Y$.  For \processes such as $b$, the last delivery
  %% is $\alpha_Y$: $d_b(\_) \rightarrow \ldots \rightarrow d_b(\alpha_X)
  %% \rightarrow \ldots \rightarrow d_b(\alpha_Y)$; For \processes such
  %% as $c$, the last delivery is $\alpha_X$, and they delivered the
  %% addition and removal of $P_Y$: $d_c(\_) \rightarrow \ldots
  %% \rightarrow d_c(\alpha_Y) \rightarrow \ldots \rightarrow
  %% d_c(\delta_Y) \rightarrow \ldots \rightarrow d_c(\alpha_X)$. Both
  %% $a$ and $d$ delivered $\alpha_X$ last: $d_a(\_) \rightarrow \ldots
  %% \rightarrow d_a(\alpha_X)$. Their difference being their position in
  %% the chain: $d$ is a child of \processes that delivered messages
  %% about $P_Y$.

  %% \begin{asparadesc}
  %% \item [($a$ or $c$ or $d$) to ($a$ or $c$ or $d$):] The source is
  %%   like $a$.  By propagating from \process to \process the
  %%   corresponding $\delta_X$ message, these \processes purge
  %%   $\alpha_X$.
  %% \item [$a$ to $b$:] $b$ stops the propagation of $\delta_X$, for the
  %%   latter does not target its current partition.
  %% \item [$b$:] They need to purge their own $P_Y$, we must \TODO{prove
  %%   that $[a, b, c, d]$ is solved and that it does not require to
  %%   purge $P_Y$.}
  %% \item [$b$ to $d$:] would deliver $d_(\alpha_y)$ hence becoming $b$.
  %% \item [$b$ to $c$:] block $d_c(\alpha_y)$, so $c$ stays in $c$. But
  %%   it detects $b$ is its parent, and possibly blocked any delta with
  %%   its value $r_b(\delta_z) \rightarrow d_b(\delta_z)$. Since not
  %%   sure, $\Delta$

  %% \item [\processes with $\alpha_X^x \rightarrow \alpha_Y^y$ with last
  %%   $\alpha_Y^y$, for $\alpha_Y^y< \alpha_X^x$:] \Processes such as
  %%   \Process~$b$ that do not directly suffer from the non-delivery of
  %%   $\delta_X$. They need to purge their own $P_Y$ if need
  %%   be. Nonetheless, they deliver and forward $\alpha_Y$ that at least
  %%   one following \process will receive.
  %% \item [\processes with $\delta_Y \rightarrow \alpha_X$:] \Processes
  %%   such as \Process~$c$ that do not belong to the preceding category,
  %%   for they already delivered $\delta_Y$. Nevertheless, best eventual
  %%   forwarding guarantees that they receive $\alpha_Y$, which
  %%   contradicts their history or state. In such a case, the detecting
  %%   \processes purge their own $\alpha_X$. The detecting \processes
  %%   must also notify subsequent \processes that their current
  %%   partition \emph{may be} deleted. Indeed their parent may have
  %%   blocked the corresponding $\delta$ messages and subsequent
  %%   \processes must purge their possibly stale state, for the sake of
  %%   consistency.  We note such a notification $\Delta_X$ to emphasize
  %%   their proximity to $\delta_X$ messages.
  %%   % the uncertainty of a $\delta$ message.
  %% \item [\processes with last $\alpha_X$ receiving $\Delta_X$ from
  %%   their parent:] \Processes such as \Process~$d$ that have
  %%   $\alpha_X$ but preceding delivered messages are not
  %%   important. Such \processes must trust detecting \processes by
  %%   delivering and forwarding $\Delta_X$. It is worth noting that
  %%   these messages are subject to all aforementioned blocking
  %%   conditions, but are also solved by aforementioned mechanisms.
  %% \end{asparadesc}

  %% Propagation~I terminates: a \process does not deliver a $\delta$
  %% message if it has already delivered it. Propagation~III terminates: a
  %% \process does not deliver a looping message.

  % ; and since \processes forward the messages they deliver, upstream
  % \processes eventually receive and may deliver messages detected as
  % issue. In Figure~\ref{fig:proofB}, \Process~$e$ eventually
  % receives $\delta_f$ from \Process~$b'$.
  Three-phase purge ensures that all \processes of the system
  eventually removes stale $\alpha$ messages, leaving room for best
  eventual forwarding of up-to-date messages.
  %
  %  \TODO{cannot loop add from $e$ , undo from $b'$ because $b'$ sent
  % delete to $e$, it will solve the inconsistency.}
  %
  %% In the meantime, \processes that still belong to a partition can
  %% propagate their respective last $\alpha$ message, and reach
  %% consistent partitioning.
\end{proof}

@@

\begin{algorithm}[h!]
  \input{input/algoascast.tex}
  \caption{\label{algo:ascast}\NAME at \Process~$p$ in dynamic networks.}
\end{algorithm}

>>>>

\begin{theorem}[\label{theo:bef}\underline{E}ventual \underline{F}orwarding
    of \underline{B}est $(EFB) \implies CP$] Assuming reliable
  communication links where a correct \process $q$ eventually receives
  the message $m$ \underline{s}ent to it by a \process $p$ ($s_{pq}(m)
  \implies r_{q}(m)$), \processes eventually reach consistent
  partitioning if each \process eventually \underline{f}orwards
  ($f_p(m) \implies \forall \langle p, q\rangle \in E: s_{pq}(m)$) its
  best known partition.
\end{theorem}

@@

\begin{proof}
  When a \process $s_1$ becomes a source, it belongs to its own
  partition, for there exists no better partition than its own:
  $\forall p \in V: |\Pi_{s_1 s_1}| < |\Pi_{s_1 p}|$. It delivers,
  hence forwards such an $\alpha$ message to its neighbors. Since
  communication links are reliable, neighboring \processes eventually
  receive such a notification $\forall \langle s_1, q \rangle \in E,
  s_1 \in S \iff \eventually r_q(\alpha_{s_1}^{w_{s_1 q}})$. Most
  importantly, whatever the order of received messages, every \process
  $q'$ in this neighborhood -- such that there exists no better
  partition $s_2$ than the received one -- delivers and forwards it:
  $\forall s_2 \in S: |\Pi_{q' s_1}| < |\Pi_{q' s_2}| \implies
  \eventually d_{q'}(\alpha_{s_1}^{w_{s_1 q'}})$. By transitivity, the
  message originating from $s_1$ reaches all such \processes through
  their shortest paths: $\forall q'' \in V, s_1, s_2 \in S: |\Pi_{q''
    s_1}| < |\Pi_{q'' s_2}| \implies \eventually
  d_{q''}(\alpha_{s_1}^{|\Pi_{s_1 q''}|})$.  Since there exists only
  one best sum of weights per \process that can never be retracted,
  \processes eventually reach consistent partitioning.
  %% /!\ not equivalence for there exists other implementations.
  %% \item [$CP \implies BEF$:] By contradiction, if a \process $q \in
  %%   \Pi_{sp} = [s, \ldots, q, q', \ldots, p]$ with $s, q, p \in P_s$
  %%   does not forward its received $\alpha_s^{|\Pi_{sq}|}$, then
  %%   following \processes from $q'$ to $p$ may mistake another
  %%   partition for their  because it needs the weight $W_{pq}$.
  %% \end{asparadesc}
\end{proof}

@@

\begin{theorem}[\label{theo:dcp}EFB$^+$: EFB $\wedge$ (Purge $\rightarrow$ EFB) $\implies$
    \underline{D}ynamic \underline{c}onsistent
    \underline{p}artitioning (DCP)]
%
When a \process can \texttt{Add} and \texttt{Del}ete its partition, to
ensure consistent partitioning, eventual forwarding of best (see
Theorem~\ref{theo:bef}) additionally requires
\begin{inparaenum}[(i)]
\item eventual purging of stale messages ($S(m)
  \implies (d_q(m) \implies \eventually d_q(m) \rightarrow
  d_q(m'))$);
\item then the eventual forwarding of best such that $m'$ ends up
  originating from the best up-to-date source for $q$.
\end{inparaenum}
\end{theorem}

\begin{proof}
  %% To reach consistent partitioning, the last message delivered by
  %% every process is not stale and comes from its respective best
  %% source: $d(m)$
  Assuming EFB as default propagation behavior where \processes
  deliver and forward the best sum of weights they received. We must
  prove that despite stale messages, the last delivery of every
  \process is the message that followed the shortest path to its
  closest source.
  \begin{asparadesc}
  \item [EFB without Purge:] From Figure~\ref{fig:problemD}, a
    \process may receive messages in such an order ($d_b(\alpha_d^1)
    \rightarrow r_b(\delta_a) \rightarrow d_b(\delta_d)$) that it does
    not forward messages required by other \processes
    ($\delta_a$). The last delivery of some nodes ($c$ and $d$) is
    wrong ($\alpha_a^3$ instead of $\delta_a$). \Processes never reach
    consistent partitioning.
    %% Figure~\ref{fig:proofA} depicts the generic case where a \process
    %% $b$ precludes itself and subsequent \processes such as $c$ of
    %% delivering the message from their respective best source
    %% $a$. \Process $b$ received and delivered a message from a
    %% partition that has since then been deleted but with a better sum
    %% of weights than newly received ones ($\alpha_d^y <
    %% \alpha_a^{x'}$). It forever discards such a message
    %% $\alpha_a^{x'}$.
  \item [Purge not followed by EFB:]
    %% also transiting messages
    Assuming that every \process removes control information as soon
    as it becomes stale ($S(\alpha_a) \implies d_b(\alpha_a^x)
    \rightarrow d_b(\delta_a)$) and cannot deliver stale messages
    anymore ($S(\alpha_a^x) \implies d_c(m_1) \rightarrow \ldots
    \rightarrow d_c(m_k \not\in \alpha_a)$), staleness does not impair
    up-to-date messages propagation. However, even in such settings,
    depending on receipt order ($d_b(\alpha_a^{x}) \rightarrow
    r_b(\alpha_c^{y : y > x}) \rightarrow d_b(\delta_b)$), a \process
    may never receive again, hence deliver and forward a message that
    was received and discarded before ($\alpha_c^{y}$). When such a
    message contains its best up-to-date partition, the \process never
    ends up in its best partition. Therefore, \processes do not reach
    consistent partitioning.
  \item [Purge then EFB:] Assuming the eventual and definitive removal
    of stale messages at each \process, eventually every \process only
    delivers and forwards up-to-date messages, or no message at
    all. Assuming that eventually, each removal triggers the
    forwarding of best delivered messages, every \process eventually
    delivers and forwards the best up-to-date delivered messages.
    %% Removing \emph{forever} all such stale messages about
    %% deleted partitions would allow \processes to propagate their best
    %% up-to-date partition again, eventually reaching consistent
    %% partitioning together, as stated by Theorem~\ref{theo:bef}.
  \end{asparadesc}
  Using EFB$^+$, \processes reach consistent partitioning together as
  in Theorem~\ref{theo:bef}.
\end{proof}

@@

\begin{theorem}[\label{theo:threephase}Three-phase purge]
  Three phases are sufficient to eventually purge the system from
  stale control information:
  \begin{inparaenum}[(i)]
  \item propagation of delete notifications,
  \item detection of possibly blocking conditions, and
  \item propagation of delete notifications that were possibly blocked.
  \end{inparaenum}
\end{theorem}

@@

  A \process (such as $d$) whose last delivery is $\alpha_X$, but
  whose parent is neither inconsistent (like $b$) nor receiving
  $\delta_X$ (like $a$), eventually receives $\Delta$ from a detecting
  \process, either directly or transitively, for such a child \process
  ($d$) trusts the possible removal of $P_X$ by delivering and
  forwarding such $\Delta$. $\Delta$ suffers from identical blocking
  conditions (between $b$ and $c$) than $\delta$, leading to the same
  solutions of detection and propagation of $\Delta$. Eventually,
  every \process whose last delivery is $\alpha_X$ receives and
  delivers either a better $\alpha_Z$, or $\delta_X$, or $\Delta_X$.
  %
  %% Some \processes may have delivered messages about other partitions
  %% before or after $\alpha_X$. \Processes such as $b$ and $c$ delivered
  %% messages about $P_Y$.  For \processes such as $b$, the last delivery
  %% is $\alpha_Y$: $d_b(\_) \rightarrow \ldots \rightarrow d_b(\alpha_X)
  %% \rightarrow \ldots \rightarrow d_b(\alpha_Y)$; For \processes such
  %% as $c$, the last delivery is $\alpha_X$, and they delivered the
  %% addition and removal of $P_Y$: $d_c(\_) \rightarrow \ldots
  %% \rightarrow d_c(\alpha_Y) \rightarrow \ldots \rightarrow
  %% d_c(\delta_Y) \rightarrow \ldots \rightarrow d_c(\alpha_X)$. Both
  %% $a$ and $d$ delivered $\alpha_X$ last: $d_a(\_) \rightarrow \ldots
  %% \rightarrow d_a(\alpha_X)$. Their difference being their position in
  %% the chain: $d$ is a child of \processes that delivered messages
  %% about $P_Y$.
  %
  %% \begin{asparadesc}
  %% \item [($a$ or $c$ or $d$) to ($a$ or $c$ or $d$):] The source is
  %%   like $a$.  By propagating from \process to \process the
  %%   corresponding $\delta_X$ message, these \processes purge
  %%   $\alpha_X$.
  %% \item [$a$ to $b$:] $b$ stops the propagation of $\delta_X$, for the
  %%   latter does not target its current partition.
  %% \item [$b$:] They need to purge their own $P_Y$, we must \TODO{prove
  %%   that $[a, b, c, d]$ is solved and that it does not require to
  %%   purge $P_Y$.}
  %% \item [$b$ to $d$:] would deliver $d_(\alpha_y)$ hence becoming $b$.
  %% \item [$b$ to $c$:] block $d_c(\alpha_y)$, so $c$ stays in $c$. But
  %%   it detects $b$ is its parent, and possibly blocked any delta with
  %%   its value $r_b(\delta_z) \rightarrow d_b(\delta_z)$. Since not
  %%   sure, $\Delta$
  %
  %% \item [\processes with $\alpha_X^x \rightarrow \alpha_Y^y$ with last
  %%   $\alpha_Y^y$, for $\alpha_Y^y< \alpha_X^x$:] \Processes such as
  %%   \Process~$b$ that do not directly suffer from the non-delivery of
  %%   $\delta_X$. They need to purge their own $P_Y$ if need
  %%   be. Nonetheless, they deliver and forward $\alpha_Y$ that at least
  %%   one following \process will receive.
  %% \item [\processes with $\delta_Y \rightarrow \alpha_X$:] \Processes
  %%   such as \Process~$c$ that do not belong to the preceding category,
  %%   for they already delivered $\delta_Y$. Nevertheless, best eventual
  %%   forwarding guarantees that they receive $\alpha_Y$, which
  %%   contradicts their history or state. In such a case, the detecting
  %%   \processes purge their own $\alpha_X$. The detecting \processes
  %%   must also notify subsequent \processes that their current
  %%   partition \emph{may be} deleted. Indeed their parent may have
  %%   blocked the corresponding $\delta$ messages and subsequent
  %%   \processes must purge their possibly stale state, for the sake of
  %%   consistency.  We note such a notification $\Delta_X$ to emphasize
  %%   their proximity to $\delta_X$ messages.
  %%   % the uncertainty of a $\delta$ message.
  %% \item [\processes with last $\alpha_X$ receiving $\Delta_X$ from
  %%   their parent:] \Processes such as \Process~$d$ that have
  %%   $\alpha_X$ but preceding delivered messages are not
  %%   important. Such \processes must trust detecting \processes by
  %%   delivering and forwarding $\Delta_X$. It is worth noting that
  %%   these messages are subject to all aforementioned blocking
  %%   conditions, but are also solved by aforementioned mechanisms.
  %% \end{asparadesc}
  %% Propagation~I terminates: a \process does not deliver a $\delta$
  %% message if it has already delivered it. Propagation~III terminates: a
  %% \process does not deliver a looping message.  
  % ; and since \processes forward the messages they deliver, upstream
  % \processes eventually receive and may deliver messages detected as
  % issue. In Figure~\ref{fig:proofB}, \Process~$e$ eventually
  % receives $\delta_f$ from \Process~$b'$.
  %% Three-phase purge ensures that all \processes of the system
  %% eventually removes stale messages, leaving room for best eventual
  %% forwarding of up-to-date messages.
  %
  %  \TODO{cannot loop add from $e$ , undo from $b'$ because $b'$ sent
  % delete to $e$, it will solve the inconsistency.}
  %
  %% In the meantime, \processes that still belong to a partition can
  %% propagate their respective last $\alpha$ message, and reach
  %% consistent partitioning.
\end{proof}

@@

\begin{algorithm}
  \input{input/algoascast.tex}
  \caption{\label{algo:ascast}\NAME at \Process~$p$ in dynamic networks.}
\end{algorithm}

### 2021-09-08 input/related_work.tex
integrate CDN but not satisfying

Content indexing services in geo-distributed infrastructures allow
\processes to retrieve specific content while leveraging the
advantages of replication. These systems mostly rely on dedicated
location services hosted by possibly remote third-party \processes; but
cutting out the middleman requires that each \process maintains its
own index in a decentralized fashion.
% This section reviews these
% approaches.

@@

\noindent Distributing this index among \processes circumvents these
issues~\cite{voronet, ipfs, mdht, squirrel, coin_19}, but still raises
locality issues where \processes
\begin{inparaenum}[(i)]
\item request to a possibly far away location service the content
  location, and then
\item request the actual content from far away replicas.
\end{inparaenum}
For instance, using \underline{d}istributed \underline{h}ash
\underline{t}ables (DHT)~\cite{ipfs, mdht, squirrel}, each \process
stores a part of the index defined by an interval between hash values.
The hash values are the keys to retrieve the associated content
location.  Before downloading any content, a \node asks for its
location using its key. After a series of round-trips between possibly
distant DHT servers, the \node gets a list of available
replicas. Contrarily to \NAME, such services do not ensure to include
the closest replica.

>>>>

Content indexing services in geo-distributed infrastructures allow
\processes to retrieve specific content while leveraging the
advantages of replication. These systems mostly rely on dedicated
location services hosted by possibly remote third-party \processes; but
cutting out the middleman requires that each \process maintains its
own index in a decentralized fashion.

@@

\noindent Distributing this index among \processes circumvents these
issues~\cite{voronet, ipfs, mdht, squirrel, triukose2011measuring,
  coin_19}, but still raises locality issues where \processes
\begin{inparaenum}[(i)]
\item request to possibly far away location services the content
  location (e.g. as in \underline{c}ontent \underline{d}elivery
  \underline{n}etworks (CDN)~\cite{triukose2011measuring} based on
  \underline{d}omain \underline{n}ame \underline{s}ystems (DNS)), and
  then
\item request the actual content from possibly far away replicas
  (e.g. as with \underline{d}istributed \underline{h}ash
  \underline{t}ables (DHT)~\cite{ipfs, mdht, squirrel}).
\end{inparaenum}
For instance, using DHTs~\cite{ipfs, mdht, squirrel}, each \process
stores a part of the index defined by an interval between hash values.
The hash values are the keys to retrieve the associated content
location.  Before downloading any content, a \node asks for its
location using its key. After a series of round-trips between possibly
distant DHT servers, the \node gets a list of available
replicas. Contrarily to \NAME, such services do not ensure to include
the closest replica.
